ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-02 paper.tex
Added todo to address comparrisson with visapp work issue, added sentence to previous work section clarifying that the visapp work was proof-of-concept and experiments reflect that

The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
However, both of these methods use passive guidance approaches that rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but there is significant lag and a reliance on a good internet connection and remote worker being available. 
Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search. 
However, this work used encoded barcodes to simulate real objects.
In this work, we are replacing the barcodes with real objects, thereby providing a complete object detection and guidance pipeline.

@@

>>>>

The issue with a marker-based approach is that it requires significant effort to place and maintain them in an environment, which is remedied by markerless systems.
However, both of these methods use passive guidance approaches that rely on the user placing the desired marker/object within the camera's view by themselves before any guidance is provided. 
VizWiz~\cite{bigham2010vizwiz} can leverage a human's understanding of the environment to guide a user to the correct location, but there is significant lag and a reliance on a good internet connection and remote worker being available. 
Previous work on the ActiVis system~\cite{lock2019active} addressed the passive guidance issue by implementing an MDP-based controller that gives the user pointing instructions to find an out-of-view object and showed that this is a viable method of object search. 
However, that work moved to establish that an MDP-based controller is indeed a viable to generate guidance instructions and reduced variability by using encoded barcodes to simulate real objects and on-screen prompts to present the guidance instructions.
In this work, we are expanding the control model and replacing the barcodes with real objects and providing audio guidance, thereby providing a complete object detection and guidance pipeline for people with vision impairments.

@@

\todo{How to relate the VISAPP work to these results? The experiments are different, so the data aren't directly comparable.}
